---
title: "Presenting Audio Stimuli With psychTestR"
author: "Hannah Merseal"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(psychTestR)
library(shiny)
```

## Getting Started

psychTestR is a new package for creating behavioral experiment interfaces using Shiny. All documentation is available at <https://pmcharrison.github.io/psychTestR/>.

Features:

- Integrates data collection and analysis in R
- Allows for a clean workflow
- Modular testing approach (easy to read!)
- Can be deployed locally or online (important in 2020)
- Open source for open science!

## Installing psychTestR

- A little tricky, will need to update several packages & restart R session several times...
- After that, open RStudio and install with devtools:

```{r install, include=TRUE, eval=FALSE}
install.packages("devtools")
devtools::install_github("pmcharrison/psychTestR")
```

- After a little brute force, you'll be ready to go!

## A simple demo

```{r demo, echo = FALSE}

make_test(list(
  text_input_page(
    label = "name", 
    prompt = "What's your name?", 
    validate = function(answer, ...) {
      if (answer == "")
        "Name cannot be left blank."
      else TRUE
    },
    on_complete = function(answer, state, ...) {
      set_global(key = "name", value = answer,
                 state = state)
    }),
  NAFC_page(
    label = "colour",
    prompt = "What's your favourite colour?",
    choices = c("Red", "Green", "Blue")),
  elt_save_results_to_disk(complete = TRUE),
  reactive_page(function(state, ...) {
    final_page(paste0("Thank you for participating, ", 
                      get_global("name", state),
                      "."))
  })))

```

## Basic units of a test
### Pages
* Data collection is performed via **pages** (similar to PsychoPy)
* Base function is `page`(can be customized)
* There are also many helper functions for creating different page types!
     + `one_button_page` (Welcome, instructions, etc.)
     + `NAFC_page` (n-alternative forced choice)
     + `text_input_page` (text input)
     + `audio_NAFC_page` (forced choice page with audio prompt)
     + `dropdown_page` (response selected from dropdown list)
     + `slider_page` (response from slider)
     + `final_page` (page that concludes the test)
* The simple demo above uses a **Text Input Page** and a **NAFC Page**:

```{r demo2, echo = TRUE, eval=FALSE}

make_test(list(
  text_input_page(
    label = "name", 
    prompt = "What's your name?", 
    validate = function(answer, ...) {
      if (answer == "")
        "Name cannot be left blank."
      else TRUE
    },
    on_complete = function(answer, state, ...) {
      set_global(key = "name", value = answer,
                 state = state)
    }),
  NAFC_page(
    label = "colour",
    prompt = "What's your favourite colour?",
    choices = c("Red", "Green", "Blue")),
  elt_save_results_to_disk(complete = TRUE),
  reactive_page(function(state, ...) {
    final_page(paste0("Thank you for participating, ", 
                      get_global("name", state),
                      "."))
  })))

```

### Timelines
* You can create a test using a collection of pages gathered into a `timeline`.
* This makes it easier to create a test with reactive pages and custom code, but you can just use the pre-made pages. 

### Making the test



